---
title: "Preprocessing of experiment da"
author: "Sidhu, Woodin, Perlman, Winter"
date: "2026-04-06"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This script preprocesses the experimental data to get it in shape for the Bayesian models.

```{r message = FALSE}
library(tidyverse)
```

Load data:

```{r message = FALSE}
E1 <- read_csv('../data/E1_raw.csv')
E2 <- read_csv('../data/E2_raw.csv')

# Show 5 random rows each:

sample_n(E1, 5) |> print(width = Inf)
sample_n(E2, 5) |> print(width = Inf)
```

Load item properties (to be used for both experiments):

```{r message = FALSE}
items <- read_csv('../data/item_properties.csv')

# POS not needed as that's already in the main tibble (`WordClass`):

items <- items |> select(-POS)

# Make column names lowercase:

colnames(items) <- str_to_lower(colnames(items))

# Show 10 random rows:

sample_n(items, 10)
```

We'll use this as the standard fill color:

```{r}
default_col <- 'darkorchid4'
```


# Overview (both experiments)

## N participants

How many participants in each experiment? (Save this in vectors for % participant exclusions later)

```{r}
E1_ppts <- E1 |> count(participant) |> nrow()
E2_ppts <- E2 |> count(participant) |> nrow()

# Show:

E1_ppts
E2_ppts
```

## Actual trials only

Check the `trials.ran` variable:

```{r}
E1 |> count(trials.ran)
E2 |> count(trials.ran)
```

**Note**: To ask David: What are the `NA`s here? General clarification on what this variable is to describe it more clearly in the script.

Keep only the ones with `trials.ran == 1`, which are the ones where stimuli were actually presented:

```{r}
E1 <- filter(E1, trials.ran == '1')
E2 <- filter(E2, trials.ran == '1')
```

## N trials

For reporting % data exclusion, we want to compute the total data before data exclusion, which is all rows minus the attention checks:

```{r}
E1_total <- E1 |> filter(WordClass != 'AttentionCheck') |> nrow()
E2_total <- E2 |> filter(WordClass != 'AttentionCheck') |> nrow()

# Show:

E1_total
E2_total
```

Close to 6,000 trials each. We'll also create `_running_total` variables that will be updated with the current total so that we can compute both % of original data and % of last exclusion at each step.

```{r}
E1_running_total <- E1_total   # will be updated
E2_running_total <- E2_total   # will be updated
```

# Data wrangling: Experiment 1

## Attention checks

How many and which participants failed at least one of the attention checks?

```{r}
E1_fails <- E1 |> 
  filter(WordClass == 'AttentionCheck' & key_resp_2.corr == 0) |> 
  pull(participant)

# Show:

E1_fails
length(E1_fails) / E1_ppts * 100
nrow(filter(E1, participant %in% E1_fails, WordClass != 'AttentionCheck')) / E1_total * 100
```

3.25% of all participants and 2.64% of all data.

Exclude these participants (ids stored in `E1_fails` vector from last chunk):

```{r}
E1 <- E1 |>
  filter(!participant %in% E1_fails)
```

Now we can get rid of the attention check rows in the main data:

```{r}
E1 <- E1 |> filter(WordClass != 'AttentionCheck')

# Update running total:

E1_running_total <- nrow(E1)
```

## Incomplete

Check how many trials each participant completed and whether there's some who didn't complete the experiment:

```{r}
E1 |> 
  count(participant) |> 
  count(n)
```

One participant has only 10 trials. Who is this?

```{r}
E1 |> 
  count(participant) |> 
  filter(n == 10)
```

Participant 90. Let's exclude them:

```{r}
# How much is that from the current E1 total and the overall total trials?

nrow(filter(E1, participant == 90)) / E1_running_total * 100
nrow(filter(E1, participant == 90)) / E1_total * 100

# Exclude:

E1 <- filter(E1, participant != 90)
```

**Note**: To ask David: Did we pre-register this? See below however that it doesn't matter in this case because another exclusion criterion (<80% same responses) captures the same participant, see below section "Same key".

How many trials do we now have per participant?

```{r}
E1 |> 
  count(participant)
```

48 trials per participant.

## Same key

We pre-registered to exclude participants who would press the same key >80% of the time.

Let's look at the distribution of % key responses.

```{r fig.width = 6, fig.height = 3.6}
E1 |> 
  count(participant, key_resp_2.keys) |> 
  mutate(prop_key = n / 48) |> 
  ggplot(aes(x = prop_key)) +
  geom_histogram() +
  theme_classic()
```

Looks like no participant has >80% responses. Check this more precisely:

```{r}
E1 |> 
  count(participant, key_resp_2.keys) |> 
  mutate(prop_key = n / 48) |> 
  filter(prop_key > 0.8 | prop_key < 0.2)
```

No participant has >80% same responses. This differs from David's original script because it turns out that this participant was also the one who didn't complete the experiment, participant 90.

```{r}
filter(E1, participant == '90')
```

Indeed, this participant is not part of the data anymore. This was the one with just 10 trials, which was all the same key.

## Response times

We pre-registered to exclude participants with average response times less than 500ms.

First, let's check the RT variable ...

```{r}
E1 |> 
  count(key_resp_2.rt) |> 
  sample_n(20)   # 20 random rows
```

... and make it numeric (renamed into `rt`):

```{r}
E1 <- E1 |> mutate(rt = as.numeric(key_resp_2.rt)) |> select(-key_resp_2.rt)
```

Compute the by-participant averages and show distribution:

```{r fig.width = 6, fig.height = 3.6}
E1_RT_avgs <- E1 |> 
  group_by(participant) |> 
  summarize(rt_m = mean(rt))

# Show distribution:

E1_RT_avgs |> 
  ggplot(aes(x = rt_m)) +
  geom_density(fill = default_col, alpha = 0.5) +
  geom_vline(xintercept = 0.5, linetype = 'dashed') + # 500ms threshold
  theme_classic()
```

Find the corresponding participant IDs:

```{r}
fast_ppts <- E1_RT_avgs |> 
  filter(rt_m <= 0.5) |> 
  pull(participant)

# Check who they are:

fast_ppts
```

Two participants are that fast: `123` and `40`.

Exclude them, check % and update totals:

```{r}
E1 <- filter(E1, !participant %in% fast_ppts)

# Check:

(1 - nrow(E1) / E1_total) * 100
(1 - nrow(E1) / E1_running_total) * 100

# Update running total:

E1_running_total <- nrow(E1)
```

**Note**: Check percentages.

## Select relevant columns

Rename relevant columns into simpler variables and reduce tibble to just those columns:

```{r}
E1 <- E1 |> 
  rename(word = Word, word_class = WordClass,
         acc = key_resp_2.corr) |> 
  select(participant, word, word_class, rt, acc)
```

## Merge item properties

Merge the item properties into the E1 tibble, reorder and rename columns:

```{r}
E1 <- E1 |> 
  left_join(items, by = c('word' = 'romaji')) |> 
  select(participant:word_class, rating:quantile, rt:acc) |> 
  rename(icon = rating)
```

## Create z-scored variables

Create z-scored variables:

```{r}
E1 <- E1 |> 
  mutate(icon_z = icon - mean(icon),
         icon_z = icon_z / sd(icon_z),
         rt_z = rt - mean(rt),
         rt_z = rt_z / sd(rt_z)) |> 
  relocate(icon_z, .after = icon) |> 
  relocate(rt_z, .after = icon)
```

## Save outside R

Show and save:

```{r}
E1
write_csv(E1, '../data/E1_processed.csv')
```

# Data wrangling: Experiment 2

## Create accuracy variable

For E2, we need to manually create an accuracy variable:

```{r}
E2 <- E2 |> 
  mutate(acc = case_when(key_resp_3.keys == CorrectKey ~ '1',
                         key_resp_3.keys != CorrectKey ~ '0'))

# Check:

select(E2, key_resp_3.keys, CorrectKey, acc)
```

Looks good.

## Attention checks

Anybody who failed attention checks?

```{r}
E2_fails <- E2 |> 
  filter(WordClass == 'AttentionCheck' & acc == 0) |> 
  pull(participant)

# Show:

E2_fails
length(E2_fails) / E2_ppts * 100
nrow(filter(E2, participant %in% E2_fails, WordClass != 'AttentionCheck')) / E2_total * 100
```

E1: 0.83% of all participants and 0.83% of all data.

Exclude these participants (ids stored in `E2_fails` vector from last chunk):

```{r}
E2 <- E2 |>
  filter(!participant %in% E2_fails)
```

Now we can get rid of the attention check rows in the main data:

```{r}
E2 <- E2 |> filter(WordClass != 'AttentionCheck')

# Update running total:

E2_running_total <- nrow(E2)
```

## Incomplete

## Not completed

Check how many trials each participant completed and whether there's some who didn't complete the experiment:

```{r}
E2 |> 
  count(participant) |> 
  count(n)
```

They all completed it all - no need to exclude anyone based on this criterion.

## Same key

We pre-registered to exclude participants who would press the same key >80% of the time.

Let's look at the distribution of % key responses.

```{r fig.width = 6, fig.height = 3.6}
E2 |> 
  count(participant, key_resp_3.keys) |> 
  mutate(prop_key = n / 48) |> 
  ggplot(aes(x = prop_key)) +
  geom_histogram() +
  theme_classic()
```

Looks like there might be one or two participants with >80% responses. Check this more precisely:

```{r}
E2 |> 
  count(participant, key_resp_3.keys) |> 
  mutate(prop_key = n / 48) |> 
  filter(prop_key > 0.8 | prop_key < 0.2)
```

Actually no, so we're good here.

## Response times

Same as for E1, pre-registered <500ms (participant average) exclusion criterion:

First, let's check the RT variable ...

```{r}
E2 |> 
  count(key_resp_3.rt) |> 
  sample_n(20)   # 20 random rows
```

... and make it numeric (renamed into `rt`):

```{r}
E2 <- E2 |> mutate(rt = as.numeric(key_resp_3.rt)) |> select(-key_resp_3.rt)
```

Compute the by-participant averages and show distribution:

```{r fig.width = 6, fig.height = 3.6}
E2_RT_avgs <- E2 |> 
  group_by(participant) |> 
  summarize(rt_m = mean(rt))

# Show distribution:

E2_RT_avgs |> 
  ggplot(aes(x = rt_m)) +
  geom_density(fill = default_col, alpha = 0.5) +
  geom_vline(xintercept = 0.5, linetype = 'dashed') + # 500ms threshold
  theme_classic()
```

Find the corresponding participant IDs:

```{r}
fast_ppts <- E2_RT_avgs |> 
  filter(rt_m <= 0.5) |> 
  pull(participant)

# Check who they are:

fast_ppts
```

This time only one participant: `66`.

Exclude them, check % and update totals:

```{r}
E2 <- filter(E2, !participant %in% fast_ppts)

# Check:

(1 - nrow(E2) / E2_total) * 100
(1 - nrow(E2) / E2_running_total) * 100

# Update running total:

E2_running_total <- nrow(E1)
```

**Note**: Check percentages.

## Select relevant columns

Rename relevant columns into simpler variables and reduce tibble to just those columns:

```{r}
E2 <- E2 |> 
  rename(word = Word, word_class = WordClass) |> 
  select(participant, word, word_class, rt, acc)
```

## Merge item properties

Merge the item properties into the E1 tibble, reorder and rename columns:

```{r}
E2 <- E2 |> 
  left_join(items, by = c('word' = 'romaji')) |> 
  select(participant:word_class, rating:quantile, rt:acc) |> 
  rename(icon = rating)
```

## Create z-scored variables

Create z-scored variables:

```{r}
E2 <- E2 |> 
  mutate(icon_z = icon - mean(icon),
         icon_z = icon_z / sd(icon_z),
         rt_z = rt - mean(rt),
         rt_z = rt_z / sd(rt_z)) |> 
  relocate(icon_z, .after = icon) |> 
  relocate(rt_z, .after = icon)
```

## Save outside R

Show and save:

```{r}
E2
write_csv(E2, '../data/E2_processed.csv')
```

