---
title: "Meta-analysis of guessing accuracy studies"
author: "Sidhu, Woodin, Perlman, Winter"
date: "2025-09-26"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro

In this script, we will perform a historical meta-analyses of the series of guessing accuracy studies that was performed under the banner of "phonetic symbolism" from the 1930's to the 1970's.

Load libraries:

```{r libraries, message = FALSE, warning = FALSE}
library(tidyverse)
library(tidybayes)
library(brms)
```

We'll use `darkorchid4` as the standard fill color:

```{r}
default_col <- 'darkorchid4'
default_col2 <- 'lightsteelblue3'
```

Load data:

```{r data_loading, message = FALSE, warning = FALSE}
met <- read_csv('../data/phonetic_symbolism_meta_analysis.csv') |> 
  select(reference, year, experiment, n_sub:accuracy) # re-order

# Show random rows:

sample_n(met, 10)
```

This data contains:

- the `reference` of the initial publication
- a numerical identifier for the `experiment` within each publication
- the publication `year`
- the number of subjects `n_sub`
- the number of trials `n_trials`
- whether the study only included `antonyms`
- the modality with which stimuli were presented: `auditory_presentation` (0 = written, 1 = auditory)
- the guessing `accuracy`, our main DV

# Preprocessing

The main DV, `accuracy`, is a percentage, which is a continuous variable that is bounded by [0%, 100%]. A sensible data-generating process for such data would be the beta distribution.

For the Bayesian beta regression model below, we'll have to convert `accuracy` to be a [0, 1] bounded variable>

```{r convert_to_01}
met <- met |> 
  mutate(acc_01 = accuracy / 100)

# Check:

met |> select(accuracy, acc_01)
```

# Overview

This sections gives an overview of the dataset, answering such questions as:

- How many publications, experiments, subjects, and trials do we have?
- How many experiments do we have?
- How many experiments included antonyms?
- How many used auditory or written presentation?

```{r n_pubs}
met |> count(reference, sort = TRUE)
```

14 studies in total.

What's the total number of experiments, and the average number of experiments?

```{r n_experiments}
met |> 
  count(reference) |> 
  summarize(total = sum(n),      # total number of experiments
            average = mean(n))   # average number of experiments
```

We have a total of 57(!) experiments in this dataset. That's quite nice.

On average, each study has about 4 experiments. The good old days!

How many subjects do we have in total? And how many subjects does each study have on average?

```{r n_sub}
met |> 
  summarize(n_total = sum(n_sub, na.rm = TRUE),
            n_average = mean(n_sub, na.rm = TRUE),
            min_sub = min(n_sub, na.rm = TRUE),
            max_sub = max(n_sub, na.rm = TRUE))
```

A total of 3,366 participants across studies, on average ~60 per experiment. The smallest study has only 29 participants, the biggest one 294.

This is an undercount because Allport (1935) does not report how many people participated in the experiment.

Let's look at the number of trials:

```{r n_trials}
met |> 
  summarize(n_total = sum(n_trials, na.rm = TRUE),
            n_average = mean(n_trials, na.rm = TRUE))
```

A total of 1627 trials across experiments (on average 28.5 per experiment), which multiplied by the number of participants yields:

```{r total_data_points}
1627 * 3366
```

Our data is based on a whopping 5,476,482 (~5.5 million) data points. Again, this must be a slight undercount given that we don't have the participant figures for Allport (1935).

How many experiments used antonyms?

```{r antonym_count}
met |> 
  count(antonyms) |> 
  mutate(p = n / sum(n),
         perc = round(p, 3) * 100,
         perc = str_c(perc, '%'))
```

More than two thirds of the studies (68.4%) tested antonyms. For 3 experiments (5.3% of the data), we do not know what kinds of stimuli were tested.

How many experiments used auditory versus written presentations?

```{r auditory_presentation_count}
met |> 
  count(auditory_presentation) |> 
  mutate(p = n / sum(n),
         perc = round(p, 3) * 100,
         perc = str_c(perc, '%'))
```

A little more than half (54.4%) used written presentation, with slightly fewer using auditory presentation (43.9%).

Let's look at whether there are more or less subjects over time, or more or less trials. We can color-code the data points for `antonyms` and map the `shape` of each point onto `auditory_presentation`.

Since we don't have subject information for Allport (1935), we can set the x-axis from 1950 to 1980:

```{r design_trends_n_sub, fig.width = 4.8, fig.height = 3.6, fig.align = 'center'}
met |> 
  filter(!is.na(antonyms),
         !is.na(auditory_presentation)) |> 
  ggplot(aes(x = year, y = n_sub)) +
  geom_point(aes(color = factor(antonyms), shape = factor(auditory_presentation))) +
  scale_x_continuous(limits = c(1950, 1975)) +
  ylab('Number of subjects') +
  theme_classic()
```

No real patterns here. Let's do the same for the number of trials:

```{r design_trends_n_trials}
met |> 
  filter(!is.na(antonyms),
         !is.na(auditory_presentation)) |> 
  ggplot(aes(x = year, y = n_trials)) +
  geom_point(aes(color = factor(antonyms), shape = factor(auditory_presentation))) +
  scale_x_continuous(limits = c(1950, 1975)) +
  ylab('Number of subjects') +
  theme_classic()
```

Also no clear trend.

# Descriptive statistics

Let's compute the average accuracy across all studies (grand average):

```{r grand_average}
met |> summarize(M = mean(accuracy))
```

The average across all studies is 56.9%.

Check descriptively whether `antonyms` makes a difference:

```{r mean_antonyms}
met |> 
  filter(!is.na(antonyms)) |> 
  group_by(antonyms) |> 
  summarize(M = mean(accuracy))
```

Studies that test antonyms are 5.2% higher in average accuracy.

Check descriptively whether `auditory_presentation` makes a difference:

```{r mean_modality}
met |> 
  filter(!is.na(auditory_presentation)) |> 
  group_by(auditory_presentation) |> 
  summarize(M = mean(accuracy))
```

Exactly equal. Doesn't seem to make any difference.

# Data visualization

## Studies over time

Make a plot of studies over time:

```{r year_plot, fig.width = 8, fig.height = 4}
# Plot core:

year_p <- met |> 
  count(year) |> 
  ggplot(aes(x = year, y = n)) +
  geom_col(fill = default_col2)

# Axes, labels and cosmetics:

year_p <- year_p +
  xlab(NULL) +
  ylab(NULL) +
  scale_x_continuous(breaks = seq(1930, 1970, 10),
                     limits = c(1930, 1975))+
  scale_y_continuous(breaks = seq(0, 20, 5),
                     limits = c(0, 20),
                     expand = c(0, 0)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 10))

# Annotations:

year_p <- year_p +
  # Allport 1935

  annotate('text', x = 1941.5, y = 3,
           label = 'Allport (1935)',
           hjust = 0.5, size = 4) +
  annotate('curve', x = 1938.2, y = 2.9,
           xend = 1935.5, yend = 1.2,
           curvature = +0.2,
           arrow = arrow(length = unit(5, 'pt')),
           linewidth = 0.5) +

  # Brown, Black & Horowitz (1955)

  annotate('text', x = 1950, y = 8 - 1,
           xend = 1954.5, yend = 3.5,
           label = 'Brown, Black & Horowitz (1955)',
           hjust = 0.5, size = 4) +
  annotate('curve', x = 1950, y = 7.5 -1,
           xend = 1954.3, yend = 2.7,
           curvature = +0.2,
           arrow = arrow(length = unit(5, 'pt')),
           linewidth = 0.5) +

  # Baindurashvili (1967) & Siegel, Silverman, & Markel (1967)

  annotate('text', x = 1966.4, y = 14.5,
           label = 'Baindurashvili (1967)\nSiegel, Silverman, & Markel (1967)',
           hjust = 1, size = 4)

# Show and save:

year_p
ggsave(plot = year_p,
       filename = '../figures/png/meta_studies_over_time.png',
       width = 8, height = 4)
```


## Average accuracy

Peaking ahead

**Note:** Change order later.

```{r}
x <- seq(35, 80, length.out = 1000)

prior_df <- tibble(accuracy = x,
                   density = dt((qlogis(x / 100) - 0) / 0.1724, df = 3) / 0.1724 * (1 / ((x / 100) * (1 - x / 100))) / 100) |> 
  mutate(density = density * 2) # scale for plot
```


Let's make a density plot of the distribution of accuracy values across studies:

```{r density_plot, fig.width = 4.8, fig.height = 3.1, fig.align = 'center'}
# Plot core:

dens_p <- met |> 
  ggplot(aes(x = accuracy)) +
  geom_density(fill = default_col2, alpha = 0.8) +
  geom_vline(xintercept = 50, linetype = 'dashed') +
  geom_rug(alpha = 0.6, length = unit(0.027, 'npc'))

# Scales, axes, and annotations:

dens_p <- dens_p +
  scale_x_continuous(limits = c(40, 80),
                     breaks = seq(40, 80, 5),
                     labels = str_c(seq(40, 80, 5), '%')) +
  # scale_y_continuous(expand = c(0, 0), limits = c(0, 0.10),
  #                    breaks = seq(0, 0.10, 0.02)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.25), # for later transition
                     breaks = seq(0, 0.25, 0.05)) +
  xlab('Accuracy (study average)') +
  # ylab('Probability density') +
  ylab(NULL) +
  NULL
  # annotate('text', x = 49.6, y = 0.09,
  #          label = '50% chance\nbaseline',
  #          hjust = 1,
  #          size = 3)

# Visualize intercept prior on this:

dens_p <- dens_p +
  geom_line(data = prior_df,
            mapping = aes(x = accuracy, y = density),
            linewidth = 1, col = 'chartreuse4')

# Plot cosmetics:

dens_p <- dens_p +
  theme_classic() +
  theme(axis.title.x = element_text(face = 'bold', margin = margin(t = 6))) +
  # theme(axis.title.y = element_text(margin = margin(r = 10))) +
  theme(axis.line.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  coord_cartesian(clip = 'off')

# Show and save:

dens_p
ggsave('../figures/pdf/meta_analysis_density_plot.pdf',
       width = 6, height = 2.8)
ggsave('../figures/png/meta_analysis_density_plot.png',
       width = 6, height = 2.8)
```

# Modeling

## Grand average, no fixed effects, unweighted

Our first beta regression model will be an intercept-only model. This is because we have one `NA` for the `antonyms` variable, and we want to know what the grand average is irrespective of any of the fixed effects.

The model will contain a `(1|reference)` random intercept, i.e., it is a random effects meta-analysis allowing for some studies to have on average higher or lower accuracies. The random effect variation is likely going to be inflated in this model because `(1|reference)` masks the contribution of the `antonyms` and `auditory_presentation` variables, e.g., some references include only antonyms (e.g., Baindurashvili 1967), and others only test non-antonyms (e.g., Brackbill and Little 1957).

In this first analysis, we'll now weight by `n_sub`, i.e., each study will be treated equally. Later we'll look at how things appear when we allow bigger studies to contribute more towards the mean using a weighted beta regression.

### Prior specification

`brms` would set a `student_t(3, 0, 2.5)` prior on the intercept by default. Let's visualize this prior:

```{r prior_viz, fig.width = 4.8, fig.height = 3.1, fig.align = 'center'}
# Plot core:

ggplot(data = tibble(x = c(-15, 15)),
       mapping = aes(x)) +
  stat_function(fun = function(x) dt((x - 0) / 2.5, df = 3) / 2.5,
                color = "lightsteelblue4",
                linewidth = 1) +
  
# Axes and labels:
  
  labs(title = "Prior for Intercept",
       y = "Density",
       x = "Intercept") +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 0.2)) +
  
# Cosmetics:
  
  theme_minimal() +
  theme(axis.line.x = element_line())
```

This is on the logit scale, since beta regression uses a `mu = logit` link. The graph suggests that this prior would seem to be very agnostic. Even very high and low logit values, e.g., -8/+8, have quite high probability mass, which would correspond to accuracies of:

```{r check_prior_assumptions}
# Check logit values -8, +8

plogis(-8)
plogis(+8)

# Check logit values -5, +5

plogis(-5)
plogis(+5)
```

Yeah, this prior definitely puts too much probability mass on extreme values.

This judgment is based on multiple factors:

- lived experience tells us that when we listen to foreign languages we don't know, we cannot really understand anything unless the languages are closely related
- Dingemanse et al. (2016), a study that tested guessing accuracy of ideophones - largely independent of this research on phonetic symbolism - achieved ~55% accuracy in a binary forced choice task, and that's for words that very iconic to native speakers, which are pretty much our "best bet" for being guessable at all
- linguistic theory tells us that form-meaning mappings are largely conventional (e.g., Saussure), and even if we assume that all words ultimately may have iconic origins, de-iconization is likely going to have eroded much of that to levels that are not accessible to foreigners

All of this warrants a tighter intercept. I'd say that as a good first bet, putting the 95% probability mass onto the range [40%, 60%] seems sensible. This basically says: all else being equal, we expect 50% chance performance in a binary forced choice task, and 60% would be surprisingly good performance for conventional words.

With a little help from our friend ChatGPT, and keeping degrees of freedom = 3 for reasonably heavy tails, we need to find the right sigma.

```{r find_sigma}
# Find sigma that is 95% at 60%:

sigma <- qlogis(0.6) / qt(0.975, df = 3)

# Check if it maps to [0.4, 0.6]:


plogis( qt(c(.025, .975), df = 3) * sigma )
```

Yup, it does. Nice. Let's visualize this prior now.

```{r updated_prior_viz, fig.width = 4.8, fig.height = 3.1, fig.align = 'center'}
# Plot core:

ggplot(data = tibble(x = c(-15, 15)),
       mapping = aes(x)) +
  stat_function(fun = function(x) dt((x - 0) / sigma, df = 3) / sigma, # new value
                color = "lightsteelblue4",
                linewidth = 1) +
  
# Axes and labels:
  
  labs(title = "Prior for Intercept",
       y = "Density",
       x = "Intercept") +
  scale_x_continuous(limits = c(-2, +2),
                     breaks = seq(-2, 2, 0.5)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 3.5)) +
  
# Cosmetics:
  
  theme_minimal() +
  theme(axis.line.x = element_line())
```

Next, let's think about the random intercept prior. As a hunch, I'd be very surprised if one study had, say, +20% more accuracy than another. But because different studies use very different sets of words, different languages (sometimes not related at all, sometimes from a different genus of the Indo-European family), and use different tasks (e.g., antonyms, which are probably easier), the accuracy variation is probably bigger.

For our intercept, sigma is at:

```{r show_sigma}
sigma
```

I'd say that a sigma double than that is probably a good first bet.

```{r check_sigma}
plogis(qt(c(.025, .975), df = 3) * (sigma * 2))
```

So, let's set the priors. For the phi parameter we will use the very agnostic `brms` default `gamma(0.01, 0.01)`:

```{r set_priors}
met_priors <- c(prior(student_t(3, 0, 0.1274067), class = 'Intercept'),
                prior(student_t(3, 0, 0.2548134), class = 'sd'),
                prior(gamma(0.01, 0.01), class = 'phi'))
```

### Fit intercept-only model

Now run the model. We set `eval = FALSE` in the code chunk options because models will be pre-compiled before knitting to save time.

Important side note: to facilitate later comparison with the weighted model, I am fitting this model without the single Allenport (1935) data point for which we are missing `n_sub`. I've checked, and it makes pretty much no difference (only a couple decimals), so our conclusions don't change much, but otherwise we can't compare the models because they'd be fitted to different datasets.

```{r fit_meta_mdl, eval = FALSE}
meta_mdl <- brm(acc_01 ~ 1 + (1|reference),
                data = filter(met, !is.na(n_sub)),
                family = Beta(),
                prior = met_priors,
                
                # MCMC settings:
                
                save_pars = save_pars(all = TRUE),
                cores = 4, chains = 4,
                iter = 12000, warmup = 4000, thin = 1,
                seed = 42)

# Save:

saveRDS(meta_mdl, file = '../models/meta_analysis_intercept_only_unweighted.rds')
```

Load this now with `eval = TRUE` so that it is available for knitting:

```{r load_meta_mdl}
meta_mdl <- readRDS('../models/meta_analysis_intercept_only_unweighted.rds')
```

Double-check that priors have been correctly applied:

```{r prior_summary_meta_mdl}
prior_summary(meta_mdl)
```

Check MCMC plots to visually assess whether chains are mixing well, as well as first plot of posterior distribution:

```{r plot_mcmc_chains}
plot(meta_mdl)
```

Looks good.

Check posterior predictive simulations:

```{r pp_check_meta_mdl}
pp_check(meta_mdl, ndraws = 100)
```

Decent.

Show the model:

```{r summarize_meta_mdl} 
meta_mdl
```

What does our model predict on the proportion scale in terms of the posterior mean and 95% credible interval?

We want the marginal posterior mean and 95% interval, integrated over the random effects distribution, not conditioning on any specific group:

```{r compute_marginal_mean_unweighted}
# Setup new data:

new_data <- tibble(group = 'NEW')

# Draws from expected value of the posterior distribution:

ep <- posterior_epred(meta_mdl,
                      newdata = new_data,
                      allow_new_levels = TRUE,
                      sample_new_levels = 'gaussian')

# Summaries:

mean(ep)              # posterior mean
quantile(ep, 0.025)   # 95% credible interval, lower bound
quantile(ep, 0.975)   # 95% credible interval, upper bound
```

The posterior mean accuracy (marginal over the random effects distribituion) is 56.7%, and we can be 95% certain that the mean lies between 45.9% and 66.5%.

What is the probability that the intercept, in its logit value, is above 50%? We'll do a simple test of same sign here - it's not clear what a sensible ROPE would be.

```{r hypothesis_meta_mdl}
hypothesis(meta_mdl, 'Intercept > 0')
```

Given this model, priors and data, we can be 100% certain that the average is above 50%, that is, 100% of all posterior samples are above that threshold.

## Weighted regression

Now we want to apply regression weights that penalize small-sample studies relative to large-sample studies, which should count more towards the mean.

```{r fit_weighted_mdl, eval = FALSE}
weighted_mdl <- brm(acc_01 | weights(n_sub) ~ 1 + (1|reference),
                    data = filter(met, !is.na(n_sub)),
                    family = Beta(),
                    prior = met_priors,
                
                    # MCMC settings:
                    
                    save_pars = save_pars(all = TRUE),
                    cores = 4, chains = 4,
                    iter = 12000, warmup = 4000, thin = 1,
                    seed = 42)

# Save:

saveRDS(weighted_mdl, file = '../models/meta_analysis_intercept_only_weighted.rds')
```

Load this now with `eval = TRUE` so that it is available for knitting:

```{r load_weighted_mdl}
weighted_mdl <- readRDS('../models/meta_analysis_intercept_only_weighted.rds')
```

Double-check that priors have been correctly applied:

```{r prior_summary_weighted_mdl}
prior_summary(weighted_mdl)
```

Check MCMC plots to visually assess whether chains are mixing well, as well as first plot of posterior distribution:

```{r plot_mcmc_chains_weighted}
plot(weighted_mdl)
```

Looks good again. The scale of the phi parameter has changed massively, but that's just because we didn't mean-center the weights and since we're not interested in phi, that's OK here.

Check posterior predictive simulations:

```{r pp_check_weighted_mdl}
pp_check(weighted_mdl, ndraws = 100)
```

Decent again.

Show the model:

```{r summarize_weighted_mdl} 
weighted_mdl
```

Same as above, marginal posterior mean and 95% interval, not conditioning on any specific group:

```{r compute_marginal_mean_weighted}
# Draws from expected value of the posterior distribution:

ep <- posterior_epred(weighted_mdl,
                      newdata = new_data,
                      allow_new_levels = TRUE,
                      sample_new_levels = 'gaussian')

# Summaries:

mean(ep)              # posterior mean
quantile(ep, 0.025)   # 95% credible interval, lower bound
quantile(ep, 0.975)   # 95% credible interval, upper bound
```

What is the probability that the intercept, in its logit value, is above 50%? We'll do a simple test of same sign here - it's not clear what a sensible ROPE would be.

```{r hypothesis_weighted_mdl}
hypothesis(weighted_mdl, 'Intercept > 0')
```

Again, super certain it's above 50%.

### Model comparison

Let's compare the weighted and unweighted models in terms of their predictive power, using LOO-CV:

```{r eval = FALSE}
# loo_unweighted <- loo(meta_mdl, reloo = TRUE)
# loo_weighted <- loo(weighted_mdl, reloo = TRUE)
# 
# saveRDS(loo_unweighted, '../models/loo_cv_objects/meta_loo_unweighted.rds')
# saveRDS(loo_weighted, '../models/loo_cv_objects/meta_loo_unweighted.rds')
```

**Note**: For `weighted_mdl`: `7 problematic observation(s) found. The model will be refit 7 times.`
**Note 2**: I *still* get this warning: `Warning messages: 1: Ignoring relative efficiencies as some were NA. See argument 'r_eff' in ?loo::loo for more details.  2: Some Pareto k diagnostic values are too high. See help('pareto-k-diagnostic') for details.`

Load and compare:

```{r eval = TRUE}
# loo_unweighted <- readRDS('../models/loo_cv_objects/meta_loo_unweighted.rds')
# loo_weighted <- readRDS('../models/loo_cv_objects/meta_loo_unweighted.rds')
# 
# loo_compare(loo_unweighted, loo_weighted)
```

**Note**: Be careful though given the warning messages above.
**Note**: With the higher post-warmup iterations it doesn't run anymore due to 500 Mb constraint. So, lots of issues with this -> we'll work with the k-fold cross-validation.

K-fold cross-validation as loo compare seems to have issues:

```{r eval = FALSE}
k10_weighted <- kfold(weighted_mdl, K = 10, save_fits = TRUE)
k10_unweighted <- kfold(meta_mdl, K = 10, save_fits = TRUE)

saveRDS(k10_weighted, '../models/loo_cv_objects/meta_k10_weighted.rds')
saveRDS(k10_unweighted, '../models/loo_cv_objects/meta_k10_unweighted.rds')
```

Load and compare:

```{r eval = TRUE}
k10_weighted <- readRDS('../models/loo_cv_objects/meta_k10_weighted.rds')
k10_unweighted <- readRDS('../models/loo_cv_objects/meta_k10_unweighted.rds')

loo_compare(k10_weighted, k10_unweighted)
```

## Model with fixed effects

### Prior specification

Let's add the antonym and auditory presentation fixed effects. This means that we now need to also specify priors for the coefficient slopes.

Here, I'm going to use the same reasonign that is explicated in `experiment_analysis` for the size of the SD of the student-t distributed prior for the slope (I did that analysis before this one). This works because we're also working with the assumption that things are around 50% and that a 10% change is a big change and should be at the fringe of our expectations (we're finding the logit value that is 40%/60%).

```{r}
met_priors_b <- c(prior(student_t(3, 0, 0.1274067), class = 'Intercept'),
                  prior(student_t(3, 0, 0.1274067), class = 'b'),
                  prior(student_t(3, 0, 0.2548134), class = 'sd'),
                  prior(gamma(0.01, 0.01), class = 'phi'))
```

### Fit fixed-effects model

As the intercept-only model has shown that the weighted model is massively preferred as per LOO-CV, we'll go ahead with that and don't consider the unweighted model anymore. From now on, all models will include regression weights for the number of subjects.

We'll want to compare the different models (with or without `antonyms` and/or `auditory_presentation`) with each other, so we need to make sure that they're fitted to the same data.

Since some tags are `NA` for either `antonyms` or `auditory_presentation`, we need to get the subset that has no `NA` for any of these:

```{r}
met_red <- met |> 
  filter(!is.na(antonyms),
         !is.na(auditory_presentation),
         !is.na(n_sub))
```

It would be nice to test the intercept (average guessing accuracy) in a model that controls for antonyms and auditory presentation. For this we want to create sum-codes that are fractional / weighted by how many cases there are, given that we have an unequal number of studies with/without antonyms or auditory presentation.

Check the percentages again in the new no-`NA` tibble:

```{r}
# Antonyms:

met_red |> 
  count(antonyms) |> 
  mutate(p = n / sum(n))

# Auditory presentation:

met_red |> 
  count(auditory_presentation) |> 
  mutate(p = n / sum(n))
```

Now assign the weighted effect coding:

```{r}
met_red <- met_red |> 
  mutate(antonyms_weighted = if_else(antonyms == 0, -0.722, +0.278),
         auditory_weighted = if_else(auditory_presentation == 0, -0.426, +0.574))

# Sanity checks:

0.278 * (-0.722) + 0.722 * (+0.278)
0.574 * (-0.426) + 0.426 * (+0.574)

with(met_red, weighted.mean(antonyms_weighted, w = rep(1, nrow(met_red))))
with(met_red, weighted.mean(auditory_weighted, w = rep(1, nrow(met_red))))
```

Looks good.

Fit the model:

```{r fit_weighted_full_mdl, eval = FALSE}
full_mdl <- brm(acc_01 | weights(n_sub) ~ 1 +
                  antonyms_weighted + auditory_weighted +
                  (1|reference),
                data = met_red,
                family = Beta(),
                prior = met_priors_b,
                
                # MCMC settings:
                    
                save_pars = save_pars(all = TRUE),
                cores = 4, chains = 4,
                iter = 12000, warmup = 4000, thin = 1,
                seed = 42)

# Save:

saveRDS(full_mdl, file = '../models/meta_full_mdl.rds')
```

Load:

```{r load_full_mdl, eval = TRUE}
full_mdl <- readRDS('../models/meta_full_mdl.rds')
```

Build the nested model without `antonyms` and without `auditory_presentation`:

```{r fit_weighted_nested_mdl, eval = FALSE}
full_no_antonym_mdl <- brm(acc_01 | weights(n_sub) ~ 1 +
                             auditory_presentation +
                             (1|reference),
                           data = met_red,
                           family = Beta(),
                           prior = met_priors_b,
                
                           # MCMC settings:
                    
                           save_pars = save_pars(all = TRUE),
                           cores = 4, chains = 4,
                           iter = 12000, warmup = 4000, thin = 1,
                           seed = 42)

full_no_auditory_mdl <- brm(acc_01 | weights(n_sub) ~ 1 +
                              antonyms +
                              (1|reference),
                            data = met_red,
                            family = Beta(),
                            prior = met_priors_b,
                
                            # MCMC settings:
                    
                            save_pars = save_pars(all = TRUE),
                            cores = 4, chains = 4,
                            iter = 4000, warmup = 2000, thin = 1,
                            seed = 42)

# Save:

saveRDS(full_no_antonym_mdl, file = '../models/full_no_antonym_mdl.rds')
saveRDS(full_no_auditory_mdl, file = '../models/full_no_auditory_mdl.rds')
```

Load:

```{r load_weighted_nested_mdl}
full_no_antonym_mdl <- readRDS(file = '../models/full_no_antonym_mdl.rds')
full_no_auditory_mdl <- readRDS(file = '../models/full_no_auditory_mdl.rds')
```

### k10 compare

Since LOO-CV turned out to be problematic for the weighted model above, we'll just do ten-fold cross-validation right away.

```{r k10_full_mdl, eval = FALSE}
k10_full <- kfold(full_mdl, K = 10, save_fits = TRUE)
k10_no_antonym <- kfold(full_no_antonym_mdl, K = 10, save_fits = TRUE)
k10_no_auditory <- kfold(full_no_auditory_mdl, K = 10, save_fits = TRUE)

saveRDS(k10_full, '../models/loo_cv_objects/meta_k10_full.rds')
saveRDS(k10_no_antonym, '../models/loo_cv_objects/meta_k10_no_antonym.rds')
saveRDS(k10_no_auditory, '../models/loo_cv_objects/meta_k10_no_auditory.rds')
```

Load k10 cross-validations:

```{r eval = TRUE}
k10_full <- readRDS('../models/loo_cv_objects/meta_k10_full.rds')
k10_no_antonym <- readRDS('../models/loo_cv_objects/meta_k10_no_antonym.rds')
k10_no_auditory <- readRDS('../models/loo_cv_objects/meta_k10_no_auditory.rds')
```

Check antonym effect:

```{r k10_antonym}
loo_compare(k10_full, k10_no_antonym)
```

Auditory presentation effect:

```{r k10_auditory}
loo_compare(k10_full, k10_no_auditory)
```

## Bayes factors

Assess Bayes factors for antonym versus full:

```{r full_v_antonym_BF, eval = FALSE}
BF_1 <- bayes_factor(full_mdl, full_no_antonym_mdl)
BF_2 <- bayes_factor(full_mdl, full_no_antonym_mdl)
BF_3 <- bayes_factor(full_mdl, full_no_antonym_mdl)

# Save:

saveRDS(BF_1, '../models/bayes_factors/meta_full_v_no_antonym_BF_1.rds')
saveRDS(BF_2, '../models/bayes_factors/meta_full_v_no_antonym_BF_2.rds')
saveRDS(BF_3, '../models/bayes_factors/meta_full_v_no_antonym_BF_3.rds')
```

Load and show:

```{r full_v_antonym_BF_load, eval = TRUE}
BF_1 <- readRDS('../models/bayes_factors/meta_full_v_no_antonym_BF_1.rds')
BF_2 <- readRDS('../models/bayes_factors/meta_full_v_no_antonym_BF_2.rds')
BF_3 <- readRDS('../models/bayes_factors/meta_full_v_no_antonym_BF_3.rds')

# Show:

BF_1
BF_2
BF_3
```

MASSIVE - but also varying on orders of magnitude. Highly volatile and can't be trusted. Need to see if upping post-warmup samples helps, but I suspect Bayes Factors will be tricky for this data.

```{r auditory_v_full_BF, eval = FALSE}
BF_1 <- bayes_factor(full_no_auditory_mdl, full_mdl)
BF_2 <- bayes_factor(full_no_auditory_mdl, full_mdl)
BF_3 <- bayes_factor(full_no_auditory_mdl, full_mdl)

# Save:

saveRDS(BF_1, '../models/bayes_factors/meta_no_auditory_v_full_BF_1.rds')
saveRDS(BF_2, '../models/bayes_factors/meta_no_auditory_v_full_BF_2.rds')
saveRDS(BF_3, '../models/bayes_factors/meta_no_auditory_v_full_BF_3.rds')
```

Load and show:

```{r auditory_v_full_BF_load, eval = TRUE}
BF_1 <- readRDS('../models/bayes_factors/meta_no_auditory_v_full_BF_1.rds')
BF_2 <- readRDS('../models/bayes_factors/meta_no_auditory_v_full_BF_2.rds')
BF_3 <- readRDS('../models/bayes_factors/meta_no_auditory_v_full_BF_3.rds')

# Show:

BF_1
BF_2
BF_3
```

These ones don't vary that much, but still a little volatile - to be interpreted for now as they all point in a similar direction, but **Note**: up post-warmup iterations to see whether this makes things more stable. Suggest mostly "meh" preference for the no auditory model.

## Interpret model

Show the full model:

```{r interpret_full_mdl}
full_mdl
```

Get the corresponding 95% interval of the interceptL

```{r}
fixef(full_mdl) |> 
  as.data.frame() |> 
  slice_head(n = 1) |> 
  mutate(estimate_p = plogis(Estimate),
         lower_ci = plogis(Q2.5),
         upper_ci = plogis(Q97.5))
```


## Posterior probabilities

Compute posterior probabilities of direction:

```{r full_mdl_post_probs}
hypothesis(full_mdl, 'Intercept > 0')
hypothesis(full_mdl, 'antonyms_weighted > 0')
hypothesis(full_mdl, 'auditory_weighted < 0')
```

# Data visualization

## Accuracy with model

Extract posterior to superimpose on the plot.

```{r}
posts_int <- as_draws_df(full_mdl) |>
  select(b_Intercept) |> 
  mutate(int = plogis(b_Intercept),
         int = int * 100)

# Show:

posts_int
```

Distribution of accuracy values with superimposed posterior for the mean accuracy:

```{r density_plot_with_post, fig.width = 4.8, fig.height = 3.1, fig.align = 'center'}
# Plot core:

dens_p <- met |> 
  ggplot(aes(x = accuracy)) +
  geom_density(fill = default_col2, alpha = 0.8) +
  # geom_line(data = prior_df,
  #           mapping = aes(x = accuracy, y = density),
  #           linewidth = 1, col = 'chartreuse4') +
  geom_density(data = posts_int,
               mapping = aes(x = int),
               fill = default_col, alpha = 0.5) +
  geom_vline(xintercept = 50, linetype = 'dashed') +
  geom_rug(alpha = 0.6, length = unit(0.024, 'npc'))

# Scales, axes, and annotations:

dens_p <- dens_p +
  scale_x_continuous(limits = c(40, 80),
                     breaks = seq(40, 80, 5),
                     labels = str_c(seq(40, 80, 5), '%')) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.25),
                     breaks = seq(0, 0.25, 0.05)) +
  xlab('Accuracy (study average)') +
  # ylab('Probability density') +
  ylab(NULL) +
  NULL
  # annotate('text', x = 49.6, y = 0.09,
  #          label = '50% chance\nbaseline',
  #          hjust = 1,
  #          size = 3)

# With 95% credible interval of the mean:

# dens_p <- dens_p +
#   geom_errorbarh(aes(xmin = 0.5223956 * 100,
#            xmax = 0.6043825 * 100,
#            y = 0.2),
#            height = 0.01)

# Plot cosmetics:

dens_p <- dens_p +
  theme_classic() +
  theme(axis.title.x = element_text(face = 'bold', margin = margin(t = 6))) +
  # theme(axis.title.y = element_text(margin = margin(r = 10))) +
  theme(axis.line.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())

# Show and save:

dens_p
ggsave('../figures/pdf/meta_analysis_density_plot_with_posts.pdf',
       width = 6, height = 2.8)
ggsave('../figures/png/meta_analysis_density_plot_with_posts.png',
       width = 6, height = 2.8)
```

## Accuracy with antonyms

Extract the posterior for intercept and antonyms and derive the predictions for the different antonym conditions from that. Do the same for auditory:

```{r antonym_posts}
# For reference:

# mutate(antonyms_weighted = if_else(antonyms == 0, -0.722, +0.278),
#          auditory_weighted = if_else(auditory_presentation == 0, -0.426, +0.574))

# Extract posteriors and calculate conditions:

posts_int <- as_draws_df(full_mdl) |>
  select(b_Intercept, b_antonyms_weighted, b_auditory_weighted) |> 
  mutate(int = plogis(b_Intercept) * 100,
         antonyms = b_Intercept + (b_antonyms_weighted * 0.278),
         no_antonyms = b_Intercept + (b_antonyms_weighted * (-0.722)),
         antonyms = plogis(antonyms) * 100,
         no_antonyms = plogis(no_antonyms) * 100)

# Show:

posts_int
```

Accuracy means with superimposed posterior for antonym and no-antonym studies.

```{r density_plot_with_antonym_posts, fig.width = 4.8, fig.height = 3.1, fig.align = 'center'}
# Plot core:

dens_p <- met |> 
  ggplot(aes(x = accuracy)) +
  # geom_density(fill = default_col2, alpha = 0.8) +
  geom_density(data = posts_int,
               mapping = aes(x = no_antonyms),
               fill = 'burlywood3', alpha = 0.5) +
  geom_density(data = posts_int,
               mapping = aes(x = antonyms),
               fill = default_col, alpha = 0.5) +
  geom_vline(xintercept = 50, linetype = 'dashed') +
  geom_rug(alpha = 0.6, length = unit(0.024, 'npc'))

# Scales, axes, and annotations:

dens_p <- dens_p +
  scale_x_continuous(limits = c(40, 80),
                     breaks = seq(40, 80, 5),
                     labels = str_c(seq(40, 80, 5), '%')) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.25),
                     breaks = seq(0, 0.25, 0.05)) +
  xlab('Accuracy (study average)') +
  ylab('Probability density') +
  ylab(NULL) +
  NULL
  # annotate('text', x = 49.6, y = 0.09,
  #          label = '50% chance\nbaseline',
  #          hjust = 1,
  #          size = 3)

# Plot cosmetics:

dens_p <- dens_p +
  theme_classic() +
  theme(axis.title.x = element_text(face = 'bold', margin = margin(t = 6))) +
  # theme(axis.title.y = element_text(margin = margin(r = 10))) +
  theme(axis.line.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())

# Show and save:

dens_p
ggsave('../figures/pdf/meta_analysis_density_plot_with_antonym_posts.pdf',
       width = 6, height = 2.8)
ggsave('../figures/png/meta_analysis_density_plot_with_antonym_posts.png',
       width = 6, height = 2.8)
```

## Conditional effects

Extract conditional effects for antonyms - these will appear like a continuous regression line because we just supplied numerical values.

```{r}
antonyms_cond <- conditional_effects(full_mdl, effects = 'antonyms_weighted')[[1]]

auditory_cond <- conditional_effects(full_mdl, effects = 'auditory_weighted')[[1]]
```

Get the first and last column:

```{r}
antonyms_cond[1, ]$estimate__
antonyms_cond[nrow(antonyms_cond), ]$estimate__

# Difference in posterior means (%):

(antonyms_cond[nrow(antonyms_cond), ]$estimate__ - antonyms_cond[1, ]$estimate__) * 100
```

## Items iconicity rating by word class

Iconicity ratings:

```{r}
items |> 
  ggplot(aes(x = pos, y = rating)) +
  geom_boxplot() +
  theme_classic()
ggsave('../figures/png/boxplot.png', width = 3.5, height = 4)
```


This completes this analysis.
